Format for lefse and run on the classes CR and tox

### 2019-11-06 scripts/01_clean_pheno.Rmd
update

final_pheno %>% 
  write_csv('../data/cleaned_pheno/final_pheno.csv')
```

>>>>

final_pheno %>% 
  write_csv('../data/cleaned_pheno/final_pheno.csv')

# write out the meta data info with tox and CR in each of the table
final_pheno %>% 
  select(Sampleid, Toxicity) %>% 
  write_csv('../data/cleaned_pheno/melody_tox_metadata.csv')
```

### 2019-11-06 scripts/18_lefse_metaphlan2_CR_tox.Rmd
update

```{r}
# keeping the leading taxa info 
spp <- read_tsv('../data/metaphlan2_result/merged_abundance_table.txt') %>% 
  # remove the rows that have strain info
  filter(!str_detect(ID, 't__')) %>% 
  # keep the rows that have species info and the header
  filter(str_detect(ID, 's__|^ID')) %>% 
  rename_all(funs(str_replace(., '_profile$','')))

@@

# write out this table 
spp %>% 
  write_tsv('../data/metaphlan2_result/merged_abundance_table_species_reordered_w_taxa.tsv')
```

@@

pheno_combi %>% 
  mutate(cat_cmd = str_glue('cat {pheno_file} ../data/metaphlan2_result/merged_abundance_table_species_reordered_w_taxa.tsv > ../data/lefse_input/spp_abundace_{combi}tsv')) %>% 
  select(cat_cmd) %>% 
  write_csv('cat_combi_spp.sh', col_names = F)
```

>>>>

```{r}
# keeping the leading taxa info 
spp <- read_tsv('../data/metaphlan2_result/merged_abundance_table.txt') %>% 
  rename_all(funs(str_replace(., '_profile$','')))

@@

# write out this table 
spp %>% 
  write_tsv('../data/metaphlan2_result/merged_abundance_table_WHOLE_reordered.tsv')
```

@@

pheno_combi %>% 
  mutate(cat_cmd = str_glue('cat {pheno_file} ../data/metaphlan2_result/merged_abundance_table_WHOLE_reordered.tsv > ../data/lefse_input/spp_abundace_{combi}tsv')) %>% 
  select(cat_cmd) %>% 
  write_csv('cat_combi_spp.sh', col_names = F)
```
